Response to reviewers

### 2025-02-02 Manuscript/ecography_reponse_letter_2.tex
response updates

% TODO: Do you think we should briefly explain why we decided to stick with 5 axes and removed TPD, rather than drop to 4 like they suggest?
We have now removed all the curves for the \texttt{TPD} metrics for any space of more than four dimensions (including the empirical space).
We added this footnote to Table 3:

>>>>

The aim of including the empirical data was not to compare the metrics directly \textit{per se} but rather to provide a second example that readers preferring real world data can hopefully relate to.
In line with the aim, we have thus decided to keep the empirical dataset to 5 dimensions, namely to hopefully link it to a paper that is currently in preparation by some of the authors (with different objectives but a same subset of the data).
Furthermore, reducing the dataset to 4 dimensions would require rerunning the full analyses which will require CPU time that we currently don't have available because of other projects using our allocated computational time.

We do agree with the reviewers point that including the \texttt{TPD} metrics that are limited to 4 dimensions can be misleading.
We have now removed all the curves for the \texttt{TPD} metrics for any space of more than four dimensions (including the empirical space).
We added this footnote to Table 3:

### 2025-02-02 Manuscript/main_ecography_R2.tex
response updates

\textbf{Aspect} & \textbf{Method} & \textbf{Name} & \textbf{Description} & \textbf{\texttt{R} function} & \textbf{Reference}\\
\hline
Richness & Trait Probability Density & Functional richness & Sum of cells where trait probability density $> 0$ & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional richness & Size (volume) of the hypervolume & \texttt{BAT::kernel.alpha} & \cite{mammola2020functional}\\
 & \cr
 & Convex Hull & Functional richness & Volume of the convex hull & \texttt{BAT::hull.alpha} & \cite{cornwell2006trait}\\
 & \cr
 & Dendrogram & Alpha diversity & Total branch length of the functional dendrogram & \texttt{BAT::alpha} & \cite{petchey2002functional,cardoso2015bat}\\
\hline
Divergence & Trait Probability Density & Divergence & Overlap between the TPD function of a single observation and the TPD function of the whole set of observations & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional dispersion  & Average distance between an observation and a sample of random points within and the probabilistic hypervolume & \texttt{BAT::kernel.dispersion} & \cite{mammola2020functional}\\
 & \cr 
 & Dendrogram & Functional dispersion & Average dissimilarity between any two observations in the dendrogram & \texttt{BAT::dispersion} & \cite{cardoso2015bat}\\
 & \cr  
 & Distances & Rao's quadratic entropy & The mean Euclidean distance between every two random pairs of species & \texttt{FD::dbFD()\$RaoQ} & \cite{botta2005rao}\\
\hline
Regularity & Trait Probability Density & Functional evenness & An index of the spread of the trait distribution compared to an even spread of the distribution (e.g. the height of bins in a histogram) & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional evenness &  Overlap between a hypervolume and an imaginary hypervolume where dimensions are evenly distributed within their possible range & \texttt{BAT::kernel.evenness} & \cite{mammola2020functional}\\
 & \cr 
 & Dendrogram & Functional evenness & Regularity of abundances and distances between observations in the tree. & \texttt{BAT::evenness} & \cite{cardoso2015bat,cardoso2024calculating}\\
 & \cr 
 & Distances & Functional evenness & Regularity of abundances and distances along the minimum spanning tree linking all observations & \texttt{FD::dbFD()\$FEve} & \cite{Laliberte2010FD,villeger2008new}\\
% TODO: comment from pedro: I think I mantioned this before, but this uses a tree, even if it is not an histogram
\hline

@@

\begin{table}
\center
\begin{tabular}{c | c | c}
\textbf{Metric type}  & \textbf{Question} & \textbf{Are we interested?}\\
\hline
Size & Is one group bigger than another one? & Yes \\
Divergence & Is one group more spread than another one? & Not really \\
Regularity & Is one group more evenly disperse in space? & Not really \\
Something else  & Does the position of a group change in space? & Yes \\
% TG: TODO: something about Beta Diversity (Pedro's comment?)
\end{tabular}
\caption{\textbf{Example of questions we can ask with the different metric types.}The categories are arbitrary and are taken from \cite{mammola2021concepts}}
\label{Tab:box2}
\end{table}

>>>>

\textbf{Aspect} & \textbf{Method} & \textbf{Name} & \textbf{Description} & \textbf{\texttt{R} function} & \textbf{Reference}\\
\hline
Richness & Trait Probability Density & Functional richness & Sum of cells where trait probability density $> 0$ & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional richness & Size (volume) of the hypervolume & \texttt{BAT::kernel.alpha} & \cite{mammola2020functional}\\
 & \cr
 & Convex Hull & Functional richness & Volume of the convex hull & \texttt{BAT::hull.alpha} & \cite{cornwell2006trait}\\
 & \cr
 & Dendrogram & Alpha diversity & Total branch length of the functional dendrogram & \texttt{BAT::alpha} & \cite{petchey2002functional,cardoso2015bat}\\
\hline
Divergence & Trait Probability Density & Divergence & Overlap between the TPD function of a single observation and the TPD function of the whole set of observations & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional dispersion  & Average distance between an observation and a sample of random points within and the probabilistic hypervolume & \texttt{BAT::kernel.dispersion} & \cite{mammola2020functional}\\
 & \cr 
 & Dendrogram & Functional dispersion & Average dissimilarity between any two observations in the dendrogram & \texttt{BAT::dispersion} & \cite{cardoso2015bat}\\
 & \cr  
 & Distances & Rao's quadratic entropy & The mean Euclidean distance between every two random pairs of species & \texttt{FD::dbFD()\$RaoQ} & \cite{botta2005rao}\\
\hline
Regularity & Trait Probability Density & Functional evenness & An index of the spread of the trait distribution compared to an even spread of the distribution (e.g. the height of bins in a histogram) & \texttt{TPD::REND}* & \cite{carmona2019trait}\\
 & \cr 
 & Kernel density hypervolume & Functional evenness &  Overlap between a hypervolume and an imaginary hypervolume where dimensions are evenly distributed within their possible range & \texttt{BAT::kernel.evenness} & \cite{mammola2020functional}\\
 & \cr 
 & Dendrogram & Functional evenness & Regularity of abundances and distances between observations in the tree. & \texttt{BAT::evenness} & \cite{cardoso2015bat,cardoso2024calculating}\\
 & \cr 
 & Dendrogram & Functional evenness & Regularity of abundances and distances along the minimum spanning tree linking all observations & \texttt{FD::dbFD()\$FEve} & \cite{Laliberte2010FD,villeger2008new}\\
\hline

@@

\begin{table}
\center
\begin{tabular}{c | c | c}
\textbf{Metric type}  & \textbf{Question} & \textbf{Are we interested?}\\
\hline
Size & Is one group bigger than another one? & Yes \\
Divergence & Is one group more spread than another one? & Not really \\
Regularity & Is one group more evenly disperse in space? & Not really \\
Something else & Does the position of a group change in space? & Yes \\
\end{tabular}
\caption{\textbf{Example of questions we can ask with the different metric types.}The categories are arbitrary and are taken from \cite{mammola2021concepts}}
\label{Tab:box2}
\end{table}
